---
title: "linear model from Web"
author: "Sakana Uthayasegar"
date: "Summer 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

```{r}
model.1 <- lm(SIMS~ARM, data=data)
plot(SIMS~ARM, data=data)
abline(model.1, col='red')
```
As arm strength increases, sims score increases.

### Numerical results

```{r}
cor(SIMS~ARM, data=data)
```
The correlation is 0.69 which shows arm strength has a relation to the sim score.


### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM, data=data)
summary.lm(model.1)
```
Both the intercept and the coefficient of ARM strength are significantly different from 0.


#### Predict at target point

```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.1, newdata, interval="predict")
```
The prediction interval is from -1.7 to 3.1 for SIM score.

  

## Model 2 SIM~GRIP

```{r}
model.2 <- lm(SIMS~GRIP, data=data)
plot(SIMS~GRIP, data=data)
abline(model.2, col='red')
```
GRIP and SIMS are scattered in the middle and increase evenly. 



### Numerical results 

```{r}
cor(SIMS~GRIP, data=data)
```
The correlation is 0.6398458 which shows arm strength has a relation to the grip.

### Inferential  (Build model.2)

```{r}
model.2 <- lm(SIMS~GRIP, data=data)
summary.lm(model.2)
```
Both the intercept and the coefficient of GRIP are significantly different from 0.
  
#### predict model.2 at target point

```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.2, newdata, interval="predict")
```
The prediction interval is from -3.1 to 2.03 for SIM score.

#### now add the model fit to our plot for model.2
  
  


## Model 3 SIM~ARM+GRIP

```{r}
model.3 <- lm(SIMS~ARM+GRIP, data=data)
plot(SIMS~ARM+GRIP, data=data)
abline(model.3, col='red')
```
N/A

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP, data=data)
```
 The correlation is 0.732 which shows arm strength and grip as a relation to the sim score.
 
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP, data=data)
summary.lm(model.3)
```
Both the intercept and the coefficient of GRIP and arm strength are significantly different from 0.

#### predict model.3 at target point

```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.3, newdata, interval="predict")
```
The prediction interval is from -2.1 to 2.43 for SIM score.

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
```{r}
anova(model.1,model.3)
``

## Informally compare Model.1 with model.2

```{r}
anova(model.2,model.3)
```

Comparing all models, model three is lesser in numbers than the other two models. 

### discussion and conclusion 
To conclude this discussion, model three would be determined as the best choice because of the lower rss rate compared to Model one and two. The null hypothesis would be rejected due to the small amount of the p value. 